\section*{Format}
\subsection*{Brief History of the Candidate}
This section should be a narrative summarizing the candidate’s activities since the last promotion and emphasizing those activities for which promotion is deserved. For candidates recently employed by Florida Tech, appropriate activities at the former employment, as well as at Florida Tech should be delineated and discussed. The current résumé contained in "Résumé" (Appendix A1) should be referenced.

The relative weighting of the dossier sections on "Teaching," "Research" and "Service" may be in any ratio mutually agreeable to the candidate, department head and dean. Once agreed on, such ratio should be stated in the department head’s nomination letter and should be the basis for consideration of the candidacy at the university level.

\subsection*{Teaching and Related Activities}
This section should begin with a brief statement of the candidate’s role in our teaching program. It should indicate any areas of special notes such as course development, unique student response, teaching awards, and/or particular effectiveness with unique groups (for example, individual instruction of graduate students or teaching large lecture classes).

Provide a general statement concerning the types of courses taught, i.e., lower-division, upper-division, and graduate-level courses, a list of courses taught in at least the three years in inverse chronological order. Identify which courses were developed by you or which had extensive new material added by you. For each course indicate enrollment, whether the course is required for majors, recommended for majors, or service for non-majors, and indicate what majors, if appropriate, and which of these courses have student-teacher evaluations available. Attach these evaluations as part of "Supporting Documentation for Teaching and Related Activities" (Appendix AII). If student comments are submitted, all students' comments in that course-section must be submitted, i.e., you cannot pick and choose.

Provide a list of graduate students supervised. List separately Ph.D. and master’s students. Give names, dissertation/thesis titles, dates of study and current employment, if known. If any postdoctoral fellows have been supervised, list names. name of fellowship or source of support and dates. Provide a statement concerning participation on graduate student committees or include in the list above, but clearly identify whom you supervised (primary thesis/dissertation advisor) and for whom you were a committee member.

The candidate should provide a statement summarizing his/her interpretation of his/her teaching role and success in teaching at Florida Tech. The statement should present a picture of yourself as a teacher describing, where appropriate, teaching practices in areas such as:
\begin{enumerate}
\item the setting and communicating of course goals;
\item overall course organization;
\item class preparation and methods used;
\item use of supplementary materials such as audiovisual aids, library, laboratory or field experiences;
\item grading your student work; and
\item your availability to students having difficulty with course materials or wishing further discussion of course topics.
\end{enumerate}

Where appropriate, comment on:

\begin{enumerate}
\item the method(s) you use to evaluate your teaching;
\item what you regard as your main strengths as a teacher;
\item what you regard as areas in which you need improvement as a teacher;
\item what you are doing to improve upon these goals;
\item course innovations or development; and
\item any other item(s) relating to teaching effectiveness
\item What evidence do you have that your students have the same picture of you?

\end{enumerate}

List academic advising activities. Either give the names of where too many, the approximate numbers of your academic undergraduate and graduate advisees. It would be helpful if you could estimate your advisees retention (conversely attrition) rate for the last several years. It is recognized that your advising is but one factor in retention, but performance significantly better than the Florida Tech average is a powerful attribute to your advising. If the graduate rate of your students over several years is known, please provide.

List other advising, such as student clubs sponsorship and other student counseling. These activities should cover the last three years or more. Provide a separate statement about this advising role and its impact on students and student programs.

\subsection{Research and Scholarly Activities}
The term "research" is used in its broad sense of intellectual inquiry. Essentially, the term "research" is used interchangeably with the term "scholarly activities."

Review briefly the highlights of your research contributions. Emphasize specific contributions to knowledge, but do not become overly technical.

Review your current and future research plans.

Review your research support history and future plans.

List in reverse chronological order externally funded grants and contracts. Include for each the sponsoring agency or company, dates and period of support, number of students supported and amounts funded. Give a separate or contiguous list of projects internally funded or unfunded.

List publications and contributions. List these publications in the following order or in chronological order indicating in the margin the appropriate category. Copies of some or all publications should be included in "Supporting Documentation for Research and Related Activities" (Appendix AIII). If too bulky, part or all of this section may be separated from the main dossier.

\begin{enumerate}
\item Books and monographs
\item Articles in refereed journals and books
\item Articles in non-refereed journals or books
\item Articles in refereed journals or books in press
\item Articles in non-refereed journals or books in press
\item Articles in refereed journals or books submitted
\item Articles in non-refereed journals or books submitted
\item Conference presentations and whether the entire paper and/or the abstract only was reviewed.
\item Published technical reports.
\item Other publications such as course manuals, guidebooks, etc.
\item List and describe briefly any disclosures of inventions or resulting patents.
\end{enumerate}

Provide a brief statement regarding the impact of these publications in the field of research. A recommended indicator of scholarly impact would be a review of the candidate’s publications citation rate. Include a statement of the ranking of these journals in the candidate’s research field.

List invited lectures of special note during the last three years.

The candidate should provide a brief statement on his/her interpretation of the role and success of his/her scholarly activities and discuss plans for future creative work and research. Comment on how you have developed yourself professionally in your discipline since your last promotion/appointment to Florida Tech.

\subsection*{Service Activities}
Provide a statement of the candidate’s department and university service for at least the last three years. List in reverse chronological order all significant university, college/school and department/program committee service. Identify your role on each committee and explain the purpose of the committee and explain the purpose of the committee if not obvious.

List committee service for other universities and national or regional educational or professional committees (e.g., review committees, accreditation committees, technical societies, etc.).

Provide a statement of the nature and impact of any unremunerated community service.

\subsection*{Documentation of Professional Practice Activities}
This section should be used for candidates to report professional activities that do not fit conveniently under the above headings. Such activities might include consulting, professional clinical practice, short-course development, etc.

List organizations, approximate level of effort and period of consulting. To the extent propriety permits, describe the consulting effort and the work product(s); e.g., reports, drawings, software, new test procedures, etc.

List short-course offerings by title, date, duration, location and approximate attendees. Describe your role as course developer and/or presenter.

\subsection*{Résumé}
The résumé should be current and detailed. If the résumé provides the information requested in the above sections, that section can reference the résumé. For example, it is not necessary to list publications in "Research and Scholarly Activities" (Section III) if the data requested is clearly given in the résumé. 

\subsection*{Supporting Documentation for Teaching and Related Activities}
Items included in the appendix could include, but not be limited to, student evaluations, peer evaluations, outlines of new courses developed and/or course or laboratory handouts (significant ones only) or manuals. Letters from former or current students could be included as well as copies of instructor/course evaluations. Peer evaluations could include letters from colleagues and/or formal peer reviews if available. Anecdotal information is valued less than is broad based, quantifiable data such as formal evaluations.

\subsection*{Supporting Documentation for Research and Related Activities}
Items in this appendix would normally include copies of papers, but could also include copies of proposal abstracts, letters of research awards, or letters of notification of honors, such as outstanding paper awards. If the list of research activities called for in "Research and Scholarly Activities" (Section III) is extensive, it could be included here and referred to in that section.

\subsection*{Supporting Documentation for Service Activities}
Items included here could be letters of commendation, copies of service reports authored by the candidate, or more detailed descriptions of service than is possible in "Service Activities" (Section IV).

\subsection*{Supporting Documentation for Professional Practice}
Items included here might include notification of professional registration, letters of commendation for consulting or clinical practice, or syllabi and manuals developed for short-courses, workshop or conferences.

\subsection*{Department Head Letter of Nomination}
This appendix will contain two important letters:

\begin{itemize}
\item A brief letter from the candidate addressed to the department head/program chair that states "This letter certifies that I have reviewed my dossier and that the entries and substantiation thereof are accurate."
\item A letter from the department head/program chair nominating the candidate for promotion. The letter should state the degree of support for the nomination in the department/program. For promotion to full professor, identifying the support of the department’s/program’s full professors is important. Copies of the faculty member’s annual goal/performance evaluations for the past three years could be included in this appendix.
\end{itemize}

\subsection*{Letters of Recommendation from Outside Reviewers}
Include a brief statement of the credentials of each person from whom letters have been solicited. It is expected that for promotion to full (associate) professor at least five (three) letters will be solicited. Include what aspect of the candidate’s performance the referee is competent to judge and why. Include all letters received. These letters should be added to the dossier by the department head/program chair after the candidate has made his/her final review of the dossier to afford the recommender’s confidentiality.

The academic unit head should write all requests for evaluations. The candidate should not solicit these letters although s/he may suggest names of references. The letters of request should clearly state what kind of an evaluation is being sought (the factors to be evaluated, the rank for which the person is being recommended and other pertinent information). Wherever reasonable, one or both of the following questions should be asked. From what you know of this person, would you recommend him/her for promotion at your institution?

Where does the candidate rank among his/her peers? As a courtesy to those being asked to write letters, a current copy of the candidate’s résumé should be sent.





\begin{table}
\label{advising}
\center
\begin{tabular}{| l | l | l | l }
Name& ID & Dept & Degree \\
Andrew Bastien & Computer Science & BS \\
Bhargav Bojedla& Computer Science & BS \\
Bradley Hull& Computer Science & BS \\
Cameron Wright& Computer Science & BS \\
Christopher Kiefer& Computer Science & BS \\
Harshitha Samudrala& Computer Science & BS \\
Jacqueline Torres& Computer Science & BS \\
Michael Gourdine& Computer Science & BS \\
Michael Stratton& Software Engineering & BS \\
Saikrishna Musthyala& Computer Science & BS \\
Smit Jesalbhai Patel& Computer Science & BS \\
Valin Vigliotti& Computer Science & BS \\
Vrutik Savaliya Dhansukhbhai& Computer Science & BS \\
Sathvik Kumar Kondur Suryakumar& Computer Science & BS \\
Baladhananagavenkata Sai Akhil Kuppala& Computer Information Systems & MS \\
Duaa Safer A Althbyani& Info Assurance/Cybersecurity & MS \\
Harshil Mayur Patel& Info Assurance/Cybersecurity & MS \\
James Riswick-Estelle& Behavior Analysis & MS \\
Justin Barnwell& Human-Centered Design & MS \\
Khetam Hijazi& Info Assurance/Cybersecurity & MS \\
Majed Aljuraysi& Computer Information Systems & MS \\
Nitin Kumar (Nitin) Bollam& Computer Information Systems & MS \\
Pei (Max) Zhou& Info Assurance/Cybersecurity & MS \\
Prathibha Mopidevi& Computer Information Systems & MS \\
Praveen Korra& Computer Information Systems & MS \\
Raed (Ed) Dallal& Info Assurance/Cybersecurity & MS \\
Ruchir Gupta& Human-Centered Design & MS \\
Sabah Mohammed H (Sabah Mohammed) Kumayt& Info Assurance/Cybersecurity & MS \\
Shivanand Gujjari& Human-Centered Design & MS \\
Srushti Nitin Ghadge& Human-Centered Design & MS \\
Tanvikumari Lalitbhai Dhankecha& Computer Information Systems & MS \\
Uditkumar Ajitkumar Nair& Human-Centered Design & MS \\
Ali Mohammad K Almashaykhi& Computer Science & PhD \\
Alita Regi& Human-Centered Design & PhD \\
Andrew Biron& Human-Centered Design & PhD \\
Bianca Ebanks& Human-Centered Design & PhD \\
Kazuhiko Momose& Human-Centered Design & PhD \\
Maria (Marifer) Sagastume Hurtado& Human-Centered Design & PhD \\
Victor Kitmanyen& Human-Centered Design & PhD \\
Warren (Lamar) Harrell& Human-Centered Design & PhD \\
Waseem Samkari& Computer Science & PhD \\
\end{tabular}
\end{table}

\newpage
